New Bayes covariant coupling methods to cope with change of priors in one-vs-one classification

### 2025-08-13 theory.tex
Proof of Ali

\emph{Canonicity} refers to requirement that the method should be natural. Borrowing an example from regression analysis, Gauss--Markov theorem states that ordinary least squares (OLS) estimate is the best linear unbiased estimate of the coefficients of a linear model. Therefore OLS  is a \emph{canonical} way to estimate parameters of a regression model.

>>>>

\emph{Canonicity} refers to requirement that the method should be natural. Borrowing an example from regression analysis, Gauss--Markov theorem states that ordinary least squares (OLS) estimator is the best linear unbiased estimator of the coefficients of a linear model. Therefore OLS  is a \emph{canonical} way to estimate parameters of a regression model.
